Article title

### 2019-07-09 NAR_DRAFT.tex
check in

\usepackage{NAR-natbib}
\bibliographystyle{unsrtnat}

% Enter dates of publication
\copyrightyear{2008}
\pubdate{31 July 2009}
\pubyear{2009}
\jvolume{37}
\jissue{12}

@@

Where $N$ is the total number of sites sequenced and $\mu$ is the per-site mutation probability.
By selecting $\alpha$ such that we are highly confident in all calls at frequencies greater than $\alpha$, we can compute $\mu$ and recompute the odds in favor of $\mathbf{H_1}$.
This improves the calibration of the model, but it is still worse than MuTect.
The final assumption embedded in the model is that all variants, regardless of allele frequency, have the same prior probability of being true variants.
Below we address this assumption.

\subsection{False positive rate control.}

We develop a method, following \citet{Efron2008}, for controlling the false positive rate.
Every site with sufficient coverage and at least 1 alternate read falls into one of two classes, they are either \textit{null} (non-variant with $\nu = 0$) or \textit{nonnull} (variant with $\nu = \hat{f}$) with prior probabilities $p_0$ and $p_1 = 1-p_0$,

$$
\begin{array}{ll}
p_0 = \textrm{P}\{\textrm{null}\} \quad & \textrm{f}_{0}(\mathbf{x}) \quad \textrm{density if null}\\
p_1 = \textrm{P}\{\textrm{nonnull}\} \quad & \textrm{f}_{1}(\mathbf{x}) \quad \textrm{density if nonnull} .
\end{array}
$$

The local, or site-specific, true positive probability $p_1$ can be estimated as the fraction of all sequenced sites that are expected to be positive.
In a neutrally evolving tumor, the number of cells is growing exponentially, and the count of variants with an allele frequency greater than a given allele frequency $f$ is \cite{Bozic2016,Williams2016a}.
$$
N(f) = \frac{N\mu}{f},
$$
Where $N$ is the total number of sites sequenced and $\mu$ is the per-site mutation probability.
The estimated fraction of all of the sites in the genome that will have a mutation with frequency $f$ is
$$
\hat{p}_1 = \frac{\int_{f_{-}}^{f_{+}} N(f)}{N} = \frac{\mu}{f - .01} -  \frac{\mu}{f + .01}
$$
and the estimated null probability $\hat{p}_0 = 1 - \hat{p}_1$.
\citet{Williams2016a} provides a full derivation for this, we are essentially computing the integral here of $N(f)$ in a small area around $f$.

@@

\begin{figure}[t]
\begin{center}
\includegraphics{NAR-fig1.eps}
\end{center}
\caption{Caption for figure within column.}
\label{NAR-fig1}
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics{NAR-fig2.eps}
\end{center}
\caption{Caption for wide figure over two columns.
\textbf{(a)} Left figure.
\textbf{(b)} Right figure (see (a)).
}
\label{NAR-fig2}
\end{figure*}

>>>>

\usepackage{NAR-natbib}
\bibliographystyle{unsrtnat}
\usepackage{color}
\newcommand{\rngcomment}[1]{{\color{red}RNG: #1}}
\newcommand{\bkmcomment}[1]{{\color{blue}BKM: #1}}
% Enter dates of publication
\copyrightyear{2008}
\pubdate{31 July 2009}
\pubyear{2009}
\jvolume{37}
\jissue{12}

@@

Where $N$ is the total number of sites sequenced and $\mu$ is the per-site mutation probability.
By selecting $\alpha$ such that we are highly confident in all calls at frequencies greater than $\alpha$, we can compute $\mu$ and recompute the odds in favor of $\mathbf{H_1}$.

%`\subsection{False positive rate control.}

%We develop a method, following \citet{Efron2008}, for controlling the false positive rate.
%Every site with sufficient coverage and at least 1 alternate read falls into one of two classes, they are either \textit{null} (non-variant with $\nu = 0$) or \textit{nonnull} (variant with $\nu = \hat{f}$) with prior probabilities $p_0$ and $p_1 = 1-p_0$,

%$$
%\begin{array}{ll}
%p_0 = \textrm{P}\{\textrm{null}\} \quad & \textrm{f}_{0}(\mathbf{x}) \quad \textrm{density if null}\\
%p_1 = \textrm{P}\{\textrm{nonnull}\} \quad & \textrm{f}_{1}(\mathbf{x}) \quad \textrm{density if nonnull} .
%\end{array}
%$$

%The local, or site-specific, true positive probability $p_1$ can be estimated as the fraction of all sequenced sites that are expected to be positive.
%In a neutrally evolving tumor, the number of cells is growing exponentially, and the count of variants with an allele frequency greater than a given allele frequency $f$ is \cite{Bozic2016,Williams2016a}.
%$$
%N(f) = \frac{N\mu}{f},
%$$
%Where $N$ is the total number of sites sequenced and $\mu$ is the per-site mutation probability.
%The estimated fraction of all of the sites in the genome that will have a mutation with frequency $f$ is
%$$
%\hat{p}_1 = \frac{\int_{f_{-}}^{f_{+}} N(f)}{N} = \frac{\mu}{f - .01} -  \frac{\mu}{f + .01}
%$$

%\bkmcomment{This is wrong. This is the cdf. I need the integral of the derivative which is the density.}
%and the estimated null probability $\hat{p}_0 = 1 - \hat{p}_1$.
%\citet{Williams2016a} provides a full derivation for this, we are essentially computing the integral here of $N(f)$ in a small area around $f$.

@@

\begin{figure}[t]
\begin{center}
\includegraphics{figures/wes_left_plot.pdf}
\end{center}
\caption{Caption for figure within column.}
\label{NAR-fig1}
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics{figures/kl_figure.png}
\end{center}
\caption{Caption for wide figure over two columns.
\textbf{(a)} Left figure.
\textbf{(b)} Right figure (see (a)).
}
\label{NAR-fig2}
\end{figure*}
